---
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    latex_engine: xelatex
bibliography: library.bib
urlcolor: black
linkcolor: black
mainfont: Times New Roman
fontsize: 12pt
geometry: margin = 1.2in
header-includes:
- \usepackage[section]{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \usepackage[spanish]{babel}
- \usepackage{booktabs}
- \usepackage{multirow}
- \usepackage{longtable}
- \usepackage{ltablex}
- \usepackage{array}
- \usepackage[normalem]{ulem}
- \useunder{\uline}{\ul}{}
- \onehalfspacing
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
---
...

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

\pagenumbering{gobble}

```{r child = 'portada.Rmd'}
```

\newpage
\pagestyle{fancy}
\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\pagenumbering{roman}

\lhead{\includegraphics[width=1cm]{Imagenes/ucv_logo.png} \parbox[b][1cm]{4cm}{\center Universidad Central de Venezuela}}

\newpage
\fancyhead[CO,CE]{Índice}
\setcounter{tocdepth}{3}
\tableofcontents

\listoffigures

\listoftables

\newpage
\pagenumbering{arabic}

\newpage
\fancyhead[CO,CE]{}

```{r child = 'cap I.Rmd'}
```

\newpage
\fancyhead[CO,CE]{}

```{r child = 'cap II.Rmd'}
```

\newpage
\fancyhead[CO,CE]{}

```{r child = 'cap III.Rmd'}
```
